Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-22 docs/supplement.Rnw
textual changes

  \section{Introduction}\label{sec:introduction}
  This document contains supplementary material to the paper `Adaptive 
  group-regularized logistic elastic net regression'. Section 
  \ref{sec:enetprior} contains extra details on the elastic net prior 
  distribution. Section \ref{sec:objectivefunction} gives the objective 
  function that is maximised in the variational Bayes procedure introduced in
  Section 3 of the Main Document. Section \ref{sec:polyagamma} gives details on
  the P{\'o}lya-Gamma parametrisation introduced in Section 3 of the Main
  Document. The derivations of the variational posterior used in the Main
  Document are shown in Section \ref{sec:variationaldistributions}. Section
  \ref{sec:computationalcomplexity} shows how we may reduce the computational
  complexity of our variational Bayes procedure. Section 
  \ref{sec:expectedloglikelihood} elaborates on the Variational Bayes expected
  joint log likelihood that is maximised to estimate the penalty multipliers as
  explained in Section 3 of the Main Document. The full procedure of the
  proposed method is shown in Section \ref{sec:fullestimationprocedure}. We
  apply our method to a study on microRNAs in colorectal cancer data 
  \cite[]{neerincx_combination_2018} in Section [! section ref here]. Finally, 
  we introduce the ridge and lasso versions of the proposed method in Section
  \ref{sec:evbridgelasso}.

@@

  We start with the computation of (\ref{eq:elboomega}). To this end we define:
  $$
  h(m_i, \omega_i) := \sum_{k=0}^{\infty} (-1)^k \frac{\Gamma(k+m_i}{k + 1}
  \frac{2k +m_i}{\sqrt{2 \pi \omega_i^3}}
  \exp\[-\frac{(2k + m_i)^2}{8 \omega_i} \].
  $$
  Let $\c = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix} \tr$. Furthermore, 
  in the following, all expectations and variances are with respect to 
  $Q^{(t)}$. Next we write out the three terms in (\ref{eq:elboomega}):
  \begin{subequations} \label{eq:elboomega2}
    \begin{align}
      \E [\log \L (\y ; \bbeta)] & = \sum_{i=1}^n \log \binom{m_i}{y_i} + 
      \y \tr \X \E [\bbeta] - \m \tr \E \left\{ \log [1 + \exp(\x_i \tr \bbeta)]
      \right\}, \\
      \E [\log \pi(\bomega | \bbeta)] & = \m \tr \E 
      \left\{ \log [1 + \exp(\x_i \tr \bbeta)] \right\} - n \log 2 - 
      \frac{1}{2} \m \tr \X \E [\bbeta] \\
      & \,\,\,\,\, - \sum_{i=1}^n \log \Gamma (m_i) - \frac{1}{2} \sum_{i=1}^n 
      [ ( \x_i \tr \E [\bbeta] )^2 + \x_i \tr \V [\bbeta] \x_i ] 
      \E [\omega_i] \\
      & \,\,\,\,\,+ \sum_{i=1}^n \E 
      \left\{ \log [ h(m_i, \omega_i) ] \right\}, \\
      \E [\log q(\bomega)] & =  \m \tr \log [1 + \exp(\c)] - n \log 2 - 
      \frac{1}{2} \m \tr \c - \sum_{i=1}^n \log \Gamma (m_i) - \frac{1}{2} 
      \sum_{i=1}^n c_i^2 \E [\omega_i] \\
      & \,\,\,\,\, + \sum_{i=1}^n \E \left\{ \log [ h(m_i, \omega_i) ] \right\},
	  \end{align}
  \end{subequations}
  where all mathematical operations on vectors and matrices are element wise. 
  After combining the terms in (\ref{eq:elboomega2}) and substituting the 
  expectations and variances given in the Main Document, several terms cancel to
  give:
  \begin{subequations} \label{eq:elboomega3}
	  \begin{align}
	    \E_{Q^{(t)}} & [\log \L (\y ; \bbeta)] + \E_{Q^{(t)}} 
	    [\log \pi(\bomega | \bbeta)] - \E_{Q^{(t)}} [\log q(\bomega)] \\ 
	    & = \sum_{i=1}^n \log \binom{m_i}{y_i} + ( \y - \frac{1}{2} \m) 
	    \tr \X \bmu^{(t)} + \m \tr \left\{ \frac{1}{2} \c^{(t)} - 
	    \log [1 + \exp(\c^{(t)})] \right\} \label{eq:elboomega4}\\
	    & \,\,\,\,\, + \frac{1}{4} \sum_{i=1}^n \frac{m_i}{c_i^{(t)}} 
	    \tanh \(\frac{c_i^{(t)}}{2} \)\left\{ (c_i^{(t)})^2 - 
	    ( \x_i \tr \bmu^{(t)} )^2 - \x_i \tr \bSigma^{(t)} \x_i \tr \right\}.
    \end{align}
  \end{subequations}

  Inspection of the updating equations in the Main Document, learns us that the 
  last term in the right-hand side of (\ref{eq:elboomega3}) equals zero, so that
  we are left with just (\ref{eq:elboomega4}). After a change of variables 
  $\psi_j = \tau_j - 1$, the two terms in (\ref{eq:elbobeta}) are as follows:
  \begin{subequations} \label{eq:elbobeta2}
	  \begin{align}
	    \E [\log \pi (\bbeta | \btau)] & = \frac{1}{2}\sum_{g=1}^G 
	    |\mathcal{G}(g)| \log \lambda'_g + \frac{p}{2} \log \lambda_2 - 
	    \frac{p}{2} \log (2 \pi) \\
	    & \,\,\,\,\, - \frac{\lambda_2}{2} \sum_{g=1}^G \lambda'_g \sum_{j \in 
	    \mathcal{G}(g)} \(1 + \frac{\lambda_1}{2 \sqrt{\lambda_2 \chi_j}}\) 
	    (\bmu_j^2 + \bSigma_{jj}) \\
	    & \,\,\,\,\, - \frac{1}{2} \sum_{j=1}^p \E [\log \psi_j] + \frac{1}{2} 
	    \sum_{j=1}^p \E [ \log(\psi_j + 1)], \\
	    \E [\log q (\bbeta )] & = -\frac{p}{2} - \frac{p}{2}\log (2 \pi) - 
	    \frac{p}{2} \log |\bSigma| .
	  \end{align}
  \end{subequations}
  We combine the terms in (\ref{eq:elbobeta2}) and arrive at the following for 
  (\ref{eq:elbobeta}):
  \begin{subequations} \label{eq:elbobeta3}
	   \begin{align}
	     \E_{Q^{(t)}} & [\log \pi (\bbeta | \btau)] - \E_{Q^{(t)}} 
	     [\log q (\bbeta )] \\ 
	     & = \frac{1}{2}\sum_{g=1}^G |\mathcal{G}(g)| \log \lambda'^{(t)}_g + 
	     \frac{p}{2} \log \lambda_2 + \frac{p}{2} \log |\bSigma^{(t)}| + 
	     \frac{p}{2} \\
	     & \,\,\,\,\, - \frac{\lambda_2}{2} \sum_{g=1}^G \lambda'^{(t)}_g 
	     \sum_{j \in \mathcal{G}(g)} \(1 + \frac{\lambda_1}{2 \sqrt{\lambda_2 
	     \chi_j^{(t)} } }\) \((\bmu^{(t)}_j)^2 + \bSigma_{jj}^{(t)}\) \\
	     & \,\,\,\,\, - \frac{1}{2} \sum_{j=1}^p \E_{Q^{(t)}} [\log \psi_j] + 
	     \frac{1}{2} \sum_{j=1}^p \E_{Q^{(t)}} [ \log(\psi_j + 1)].
	  \end{align}
  \end{subequations}

@@

  \section{The P\'{o}lya-Gamma parametrisation}\label{sec:polyagamma}
  In Section 3 of the Main Document latent P\'{o}lya-Gamma distributed variables
  are introduced. Likewise, in \cite{polson_bayesian_2013}, P\'{o}lya-Gamma
  variables are introduced into the logistic regression model under a Gaussian
  prior. Here, we explain how introduction of these latent variables simplifies
  the variational Bayes calculations.

@@

  \section{Computational complexity}\label{sec:computationalcomplexity}
  Calculation of $\bSigma$ involves the inversion of a 
  $(p \times p)$-dimensional matrix, which occurs at every iteration of the
  algorithm. If naively done, every inversion is of computational complexity
  $\mathcal{O}(p^3)$. With $p$ large, this is a serious computational bottleneck
  of the algorithm, especially with possibly many iterations. However, 
  inspection of the updating equations in (3.9) in the main document, reveals
  that we only require the inner products $\x_i \tr \bSigma \x_i$, $\x_i 
  \tr \bmu$, and $\bmu$, plus the diagonal of $\bSigma$ to directly update the
  $c_i$ and $\chi_j$. In Section 2.2 of the main document we show that for the 
  EM updates of $\blambda'$, we only require the $c_i$, the $\chi_j$, $\bmu$, 
  and the diagonal of $\bSigma$. Here we provide details on how to compute these
  with complexity $\mathcal{O}(n^2 p)$, thereby considerably reducing the
  computational cost of the algorithm. If necessary, we may calculate the full
  $\bSigma$ once after the algorithm has converged.

@@

  \section{Full estimation procedure}\label{sec:fullestimationprocedure}
  The expectation and maximisation steps introduced in the Main Document result
  in a procedure as outlined in Algorithm \ref{alg:summaryalg}:
  \begin{algorithm}
    \caption{Group-regularized empirical Bayes elastic net}
    \label{alg:summaryalg}
	  \begin{algorithmic}[h]
		  \Require $\X, \y, \G, \alpha, \epsilon_1, \epsilon_2$
		  \Ensure $\lambda, \blambda', \bSigma, \bmu$
		  \State{Estimate $\lambda$ by cross-validation of the regular elastic net
		  model}
		  \While{$|\frac{\blambda'^{(k + 1)} - \blambda'^{(k)}}{\blambda'^{(k)}}| >
		  \epsilon_1$}
		  \While{$\underset{ij}{\max} \, |\frac{\bSigma_{ij}^{(k+1)} - 
		  \bSigma_{ij}^{(k)}}{\bSigma_{ij}^{(k)}}| > \epsilon_2$ or 
		  $\underset{i}{\max} \, |\frac{\bmu_{i}^{(k+1)} - 
		  \bmu_{i}^{(k)}}{\bmu_{i}^{(k)}}| > \epsilon_2$}
		  \State{Update $\bSigma$, $\bmu$, $c_i$ for $i=1, \dots, n$ and $\chi_j$ 
		  for $j=1, \dots, p$ using (3.9) in the Main Document}
		  \EndWhile
		  \State{Update $\blambda'$ by (3.10) in the Main Document}
		  \EndWhile
	  \end{algorithmic}
  \end{algorithm}

@@

  A natural way of enforcing monotonicity is to extend the constraint in (10) in
  the Main Document with $\lambda'_1 \leq \dots \leq \lambda'_G$. The problem is
  still convex and may be numerically solved. From experience, however, we note
  that in combination with this constrained optimisation, the EM algorithm
  described in Section~3 in the Main Document often converges to a local optimum
  close to the initialisation. We therefore enforce monotonicity through a
  \textit{post hoc} isotonic regression on the penalty multipliers after every
  optimisation step.

@@

  \section{Application to MicroRNAs in colorectal cancer}\label{sec:colorectal}
  \subsection{Additional comparisons}
  We compared \texttt{gren} to two methods in addition to the ones in the MD: 
  the sparse group lasso (\texttt{SGL}) by \cite{simon_sparse-group_2013} and 
  the group exponential lasso (\texttt{gel}) by \cite{breheny_group_2015}. For
  all methods with a tuning parameter $\alpha$, we set 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$ and present the AUC and Brier skill score 
  on the test set in Figures 
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_auc}--
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_briers}.
<<lines_micrornaseq_colorectal_cancer_res1_auc, fig.cap="Estimated AUC for the colorectal cancer example.", out.width="100%", fig.asp=1>>=
@

@@

  \subsection{Random groups}
  Considering that the features may be partitioned into many groups, with one 
  parameter per group, we have to be aware of overfitting risks. We investigated
  this using the data introduced in Section [! section ref here] of the MD, 
  randomly dividing the features into three groups. We fixed the group sizes to 
  the group sizes used in the MD. Under this random 
  partitioning of the features, we expect all penalty multipliers to be 
  estimated as one if no overfitting occurs.

@@

  \section{Application to RNAseq in lymph node cancer}
  \label{sec:lymphnode}
  In addition to the results presented in Section [! section ref here] of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs and Brier skill 
  scores calculated on the
  validation set are presented in Figures 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}--
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_briers}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

>>>>

  \section{Introduction}\label{sec:introduction}
  This document contains supplementary material to the paper `Adaptive 
  group-regularized logistic elastic net regression'. Section 
  \ref{sec:enetprior} contains extra details on the elastic net prior 
  distribution. Section \ref{sec:objectivefunction} gives the objective 
  function that is maximised in the variational Bayes procedure introduced in
  Section \ref{md-sec:estimation} of the Main Document (MD). Section
  \ref{sec:polyagamma} gives details on
  the P{\'o}lya-Gamma parametrisation introduced in Section 
  \ref{md-sec:estimation} of the MD. The
  derivations of the variational posterior used in the MD are shown in Section
  \ref{sec:variationaldistributions}. Section
  \ref{sec:computationalcomplexity} shows how we may reduce the computational
  complexity of our variational Bayes procedure. Section 
  \ref{sec:expectedloglikelihood} elaborates on the Variational Bayes expected
  joint log likelihood that is maximised to estimate the penalty multipliers as
  explained in Section \ref{md-sec:estimation} of the MD. The full procedure of
  the
  proposed method is shown in Section \ref{sec:fullestimationprocedure}. 
  Additional results to the applications in the MD Sections 
  \ref{md-sec:colorectal}--\ref{md-sec:lymphnode}. We
  apply our method to a study on metabolomics in Alzheimer's in Section
  \ref{sec:alzheimer} and to study in microRNAs in cervical cancer data 
  in Section \ref{sec:cervical}. Finally, 
  we introduce the ridge and lasso versions of the proposed method in Section
  \ref{sec:evbridgelasso}.

@@

  We start with the computation of (\ref{eq:elboomega}). To this end we define:
  $$
  h(m_i, \omega_i) := \sum_{k=0}^{\infty} (-1)^k \frac{\Gamma(k+m_i}{k + 1}
  \frac{2k +m_i}{\sqrt{2 \pi \omega_i^3}}
  \exp\[-\frac{(2k + m_i)^2}{8 \omega_i} \].
  $$
  Let $\c = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix} \tr$. Furthermore, 
  in the following, all expectations and variances are with respect to 
  $Q^{(t)}$. Next we write out the three terms in (\ref{eq:elboomega}):
  \begin{subequations} \label{eq:elboomega2}
    \begin{align}
      \E [\log \L (\y ; \bbeta)] & = \sum_{i=1}^n \log \binom{m_i}{y_i} + 
      \y \tr \X \E [\bbeta] - \m \tr \E \left\{ \log [1 + \exp(\x_i \tr \bbeta)]
      \right\}, \\
      \E [\log \pi(\bomega | \bbeta)] & = \m \tr \E 
      \left\{ \log [1 + \exp(\x_i \tr \bbeta)] \right\} - n \log 2 - 
      \frac{1}{2} \m \tr \X \E [\bbeta] \\
      & \,\,\,\,\, - \sum_{i=1}^n \log \Gamma (m_i) - \frac{1}{2} \sum_{i=1}^n 
      [ ( \x_i \tr \E [\bbeta] )^2 + \x_i \tr \V [\bbeta] \x_i ] 
      \E [\omega_i] \\
      & \,\,\,\,\,+ \sum_{i=1}^n \E 
      \left\{ \log [ h(m_i, \omega_i) ] \right\}, \\
      \E [\log q(\bomega)] & =  \m \tr \log [1 + \exp(\c)] - n \log 2 - 
      \frac{1}{2} \m \tr \c - \sum_{i=1}^n \log \Gamma (m_i) - \frac{1}{2} 
      \sum_{i=1}^n c_i^2 \E [\omega_i] \\
      & \,\,\,\,\, + \sum_{i=1}^n \E \left\{ \log [ h(m_i, \omega_i) ] \right\},
	  \end{align}
  \end{subequations}
  where all mathematical operations on vectors and matrices are element wise. 
  After combining the terms in (\ref{eq:elboomega2}) and substituting the 
  expectations and variances, several terms cancel to
  give:
  \begin{subequations} \label{eq:elboomega3}
	  \begin{align}
	    \E_{Q^{(t)}} & [\log \L (\y ; \bbeta)] + \E_{Q^{(t)}} 
	    [\log \pi(\bomega | \bbeta)] - \E_{Q^{(t)}} [\log q(\bomega)] \\ 
	    & = \sum_{i=1}^n \log \binom{m_i}{y_i} + ( \y - \frac{1}{2} \m) 
	    \tr \X \bmu^{(t)} + \m \tr \left\{ \frac{1}{2} \c^{(t)} - 
	    \log [1 + \exp(\c^{(t)})] \right\} \label{eq:elboomega4}\\
	    & \,\,\,\,\, + \frac{1}{4} \sum_{i=1}^n \frac{m_i}{c_i^{(t)}} 
	    \tanh \(\frac{c_i^{(t)}}{2} \)\left\{ (c_i^{(t)})^2 - 
	    ( \x_i \tr \bmu^{(t)} )^2 - \x_i \tr \bSigma^{(t)} \x_i \tr \right\}.
    \end{align}
  \end{subequations}

  Inspection of the updating equations in the MD, learns us that the 
  last term in the right-hand side of (\ref{eq:elboomega3}) equals zero, so that
  we are left with just (\ref{eq:elboomega4}). After a change of variables 
  $\psi_j = \tau_j - 1$, the two terms in (\ref{eq:elbobeta}) are as follows:
  \begin{subequations} \label{eq:elbobeta2}
	  \begin{align}
	    \E [\log \pi (\bbeta | \btau)] & = \frac{1}{2}\sum_{g=1}^G 
	    |\mathcal{G}(g)| \log \lambda'_g + \frac{p}{2} \log \lambda_2 - 
	    \frac{p}{2} \log (2 \pi) \\
	    & \,\,\,\,\, - \frac{\lambda_2}{2} \sum_{g=1}^G \lambda'_g \sum_{j \in 
	    \mathcal{G}(g)} \(1 + \frac{\lambda_1}{2 \sqrt{\lambda_2 \chi_j}}\) 
	    (\bmu_j^2 + \bSigma_{jj}) \\
	    & \,\,\,\,\, - \frac{1}{2} \sum_{j=1}^p \E [\log \psi_j] + \frac{1}{2} 
	    \sum_{j=1}^p \E [ \log(\psi_j + 1)], \\
	    \E [\log q (\bbeta )] & = -\frac{p}{2} - \frac{p}{2}\log (2 \pi) - 
	    \frac{p}{2} \log |\bSigma| .
	  \end{align}
  \end{subequations}
  We combine the terms in (\ref{eq:elbobeta2}) and arrive at the following for 
  (\ref{eq:elbobeta}):
  \begin{subequations} \label{eq:elbobeta3}
	   \begin{align}
	     \E_{Q^{(t)}} & [\log \pi (\bbeta | \btau)] - \E_{Q^{(t)}} 
	     [\log q (\bbeta )] \\ 
	     & = \frac{1}{2}\sum_{g=1}^G |\mathcal{G}(g)| \log \lambda'^{(t)}_g + 
	     \frac{p}{2} \log \lambda_2 + \frac{p}{2} \log |\bSigma^{(t)}| + 
	     \frac{p}{2} \\
	     & \,\,\,\,\, - \frac{\lambda_2}{2} \sum_{g=1}^G \lambda'^{(t)}_g 
	     \sum_{j \in \mathcal{G}(g)} \(1 + \frac{\lambda_1}{2 \sqrt{\lambda_2 
	     \chi_j^{(t)} } }\) \((\bmu^{(t)}_j)^2 + \bSigma_{jj}^{(t)}\) \\
	     & \,\,\,\,\, - \frac{1}{2} \sum_{j=1}^p \E_{Q^{(t)}} [\log \psi_j] + 
	     \frac{1}{2} \sum_{j=1}^p \E_{Q^{(t)}} [ \log(\psi_j + 1)].
	  \end{align}
  \end{subequations}

@@

  \section{The P\'{o}lya-Gamma parametrisation}\label{sec:polyagamma}
  In Section \ref{md-sec:estimation} of the MD latent P\'{o}lya-Gamma
  distributed variables
  are introduced. Likewise, in \cite{polson_bayesian_2013}, P\'{o}lya-Gamma
  variables are introduced into the logistic regression model under a Gaussian
  prior. Here, we explain how introduction of these latent variables simplifies
  the variational Bayes calculations.

@@

  \section{Computational complexity}\label{sec:computationalcomplexity}
  Calculation of $\bSigma$ involves the inversion of a 
  $(p \times p)$-dimensional matrix, which occurs at every iteration of the
  algorithm. If naively done, every inversion is of computational complexity
  $\mathcal{O}(p^3)$. With $p$ large, this is a serious computational bottleneck
  of the algorithm, especially with possibly many iterations. However, 
  inspection of the updating equations in (\ref{md-eq:VBupdateequations})
  in the MD, reveals
  that we only require the inner products $\x_i \tr \bSigma \x_i$, $\x_i 
  \tr \bmu$, and $\bmu$, plus the diagonal of $\bSigma$ to directly update the
  $c_i$ and $\chi_j$. In Section \ref{md-sec:estimation} of the MD we show that 
  for the 
  EM updates of $\blambda'$, we only require the $c_i$, the $\chi_j$, $\bmu$, 
  and the diagonal of $\bSigma$. Here we provide details on how to compute these
  with complexity $\mathcal{O}(n^2 p)$, thereby considerably reducing the
  computational cost of the algorithm. If necessary, we may calculate the full
  $\bSigma$ once after the algorithm has converged.

@@

  \section{Full estimation procedure}\label{sec:fullestimationprocedure}
  The expectation and maximisation steps introduced in the Main Document Section
  \ref{md-sec:estimation} result
  in a procedure as outlined in Algorithm \ref{alg:summaryalg}:
  \begin{algorithm}
    \caption{Group-regularized empirical Bayes elastic net}
    \label{alg:summaryalg}
	  \begin{algorithmic}[h]
		  \Require $\X, \y, \G, \alpha, \epsilon_1, \epsilon_2$
		  \Ensure $\lambda, \blambda', \bSigma, \bmu$
		  \State{Estimate $\lambda$ by cross-validation of the regular elastic net
		  model}
		  \While{$|\frac{\blambda'^{(k + 1)} - \blambda'^{(k)}}{\blambda'^{(k)}}| >
		  \epsilon_1$}
		  \While{$\underset{ij}{\max} \, |\frac{\bSigma_{ij}^{(k+1)} - 
		  \bSigma_{ij}^{(k)}}{\bSigma_{ij}^{(k)}}| > \epsilon_2$ or 
		  $\underset{i}{\max} \, |\frac{\bmu_{i}^{(k+1)} - 
		  \bmu_{i}^{(k)}}{\bmu_{i}^{(k)}}| > \epsilon_2$}
		  \State{Update $\bSigma$, $\bmu$, $c_i$ for $i=1, \dots, n$ and $\chi_j$ 
		  for $j=1, \dots, p$ using (\ref{md-eq:VBupdateequations}) in the MD}
		  \EndWhile
		  \State{Update $\blambda'$ by (\ref{md-eq:mmlupdateequation}) in the MD}
		  \EndWhile
	  \end{algorithmic}
  \end{algorithm}

@@

  A natural way of enforcing monotonicity is to extend the constraint in (10) in
  the Main Document with $\lambda'_1 \leq \dots \leq \lambda'_G$. The problem is
  still convex and may be numerically solved. From experience, however, we note
  that in combination with this constrained optimisation, the EM algorithm
  described in Section \ref{md-sec:estimation} in the MD often converges to a
  local optimum
  close to the initialisation. We therefore enforce monotonicity through a
  \textit{post hoc} isotonic regression on the penalty multipliers after every
  optimisation step.

@@

  \section{Application to MicroRNAs in colorectal cancer}\label{sec:colorectal}
  \subsection{Additional comparisons}
  We compared \texttt{gren} to two methods in addition to the ones in the MD
  Section \ref{md-sec:colorectal}: 
  the sparse group lasso (\texttt{SGL}) by \cite{simon_sparse-group_2013} and 
  the group exponential lasso (\texttt{gel}) by \cite{breheny_group_2015}. For
  all methods with a tuning parameter $\alpha$, we set 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$ and present the AUC and Brier skill score 
  on the test set in Figures 
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_auc}--
  \ref{fig:lines_micrornaseq_colorectal_cancer_res1_briers}.
<<lines_micrornaseq_colorectal_cancer_res1_auc, fig.cap="Estimated AUC for the colorectal cancer example.", out.width="100%", fig.asp=1>>=
@

@@

  \subsection{Random groups}\label{sec:randomgroups}
  Considering that the features may be partitioned into many groups, with one 
  parameter per group, we have to be aware of overfitting risks. We investigated
  this using the data introduced in Section \ref{md-sec:colorectal} of the MD, 
  randomly dividing the features into three groups. We fixed the group sizes to 
  the group sizes used in the MD. Under this random 
  partitioning of the features, we expect all penalty multipliers to be 
  estimated as one if no overfitting occurs.

@@

  \section{Application to RNAseq in lymph node cancer}
  \label{sec:lymphnode}
  In addition to the results presented in Section \ref{md-sec:lymphnode} of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs and Brier skill 
  scores calculated on the
  validation set are presented in Figures 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}--
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_briers}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@
